Modeling Interactions of Ions with Ether- and Ester-linked Phospholipids

### 2019-09-25 paper.tex
Finaler

\documentclass[12pt,openany,final]{book}
\usepackage[letterpaper,margin=1in,footskip=0.25in]{geometry}
\fontfamily{cmr}
\usepackage[final]{changes}
\usepackage{lipsum}
\usepackage[nottoc]{tocbibind}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{flafter}
\usepackage{floatrow}
%\usepackage{floatflt}
\usepackage{placeins}
\usepackage{siunitx}
\usepackage{graphicx}
\graphicspath{{figures/}}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{appendix}
\usepackage{amsmath}
\usepackage{cases}
\usepackage{calc}
\usepackage{amssymb}
\usepackage{color}
\usepackage{enumitem}
\usepackage{soul}
\usepackage{indentfirst}
\usepackage{hyphenat}
\usepackage{xspace}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{lineno}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[superscript]{cite}
\usepackage{lineno}
\titleformat
{\chapter} % command
[display] % shape
{\sc\LARGE} % format
{Chapter \thechapter} % label
{0.2ex} % sep
{
} % before-code
\titlespacing*{\chapter}{0pt}{1in}{0pt}
\titlespacing*{\section}{0pt}{0pt}{0pt}
\hbadness=99999
%\epstopdfDeclareGraphicsRule{.tga}{png}{.png}{
%    convert #1 \OutputFile
%}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}
%\newcommand{\cmpersec}{$\frac{\text{cm}}{\text{s}}$~}
\newcommand{\cmpersec}{cm/s~}
\newcommand{\etal}{\textit{et al.}}
\newcommand{\na}{Na\textsuperscript{+}~}
\newcommand{\cl}{Cl\textsuperscript{-}~}
\newcommand{\PM}{$\pm$~}
\newcommand{\invnm}{$\text{\si{\nm}}^{-1}$~}
\newcommand{\nmeter}{\si{\nm}~}
\renewcommand{\arraystretch}{1.8}
%\newcommand{\hl}{\added}
%\newcommand{\sout}{\deleted}
\newcommand{\TODO}{\hl{TODO}~}
\newcommand{\about}{$\sim$}
\newcommand{\aangstroms}{{\aa}ngstr{\"o}ms}
\newcommand{\aangstrom}{{\aa}ngstr{\"o}m}
\newenvironment{hle}{\color{red}}

@@

Polar lipids, or phospholipids, are present in all parts of cells
and are used in many signalling and structural roles.
As structural molecules they act as the main component of cellular plasma membranes --- bilayers
of polar lipids that separate cells from their environments. Bilayer properties are heavily
influenced by the structure of their component polar lipids, and different lipids
are found in different organisms. 
A distinguishing feature of Archaeal plasma membranes is that their phospholipids contain ether-links, as opposed to bacterial and eukaryotic plasma
membranes where phospholipids primarily contain ester-links. In our work we examine the effects of
salt on bilayer structure in the case of an ether-linked lipid bilayer. We use molecular dynamics simulations and compare equilibrium properties of two model lipid
bilayers in NaCl salt solution --- POPC and its ether-linked analog that we refer to as HOPC. We make the following key observations.
The headgroup region of HOPC ``adsorbs'' fewer ions compared to the headgroup region of POPC. Consistent with this,
we note that the Debye screening length in the HOPC system is \about 10\% shorter than that
in the POPC system. Herein, we introduce a protocol to identify the lipid-water interfacial boundary that
reproduces the bulk salt distribution consistent with
Gouy-Chapman theory. We also note that the HOPC bilayer has excess solvent
in the headgroup region when compared to POPC,
coinciding with a trough in the electrostatic potential. Waters in
this region have longer autocorrelation times and smaller lateral diffusion rates compared to the corresponding region
in the POPC bilayer, suggesting that the waters in HOPC are more strongly
coordinated to the lipid headgroups. Furthermore, we note that it is this
region of tightly coordinated waters in the HOPC system that has a lower density of Na$^+$ ions.
Based on these observations we conclude that an ether-linked lipid bilayer has a lower binding
affinity for Na$^+$ compared to an ester-linked lipid bilayer.

@@

\section{Ether- and Ester-linked Phospholipids}
Phospholipids are a diverse species of biological molecules used in many roles in life~\cite{van:2008:lipidvariety}. These molecules
are amphipathic, with a headgroup that is hydrophillic attached to hydrophobic acyl chains by a
glycerol backbone~\cite{pandit:2008:simulationtextbook,israelachvili:2011:intermol}. 
These molecules, when above a critical concentration in aqueous solution, self assemble into
various aggregate structures in order 
to reduce the exposure of the hydrophobic chains
to polar solvent --- these structures include
micelles, vesicles, and bilayers along with others~\cite{israelachvili:2011:intermol}. 
Phospholipids tend to form bilayers, 
where the hydrophillic headgroups face the solvent and the 
hydrophobic acyl chains face into the center 
of the structure~\cite{israelachvili:2011:intermol,ashrafuzzaman:2012:membrane}. 
An image of a bilayer of a commonly studied
model lipid can be seen
in figure~\ref{fig:boximage}.
\begin{figure}[p]
    \caption[Image of a model bilayer of phospholipids from a simulation.]{ Image of a model bilayer of phospholipids from a simulation. The lipids can be seen
in the center of the image, with the hydrophobic chains colored in
light purple. The polar headgroup can be seen highlighted by the phosphate group in orange and the choline nitrogen in blue
facing the solvent. Solvent molecules have been removed for clairity. Figure generated
using VMD~\cite{vmd}}
\label{fig:boximage}
\includegraphics[width=\textwidth]{images/popc_image}
\end{figure}
In living cells, lipid bilayers act as the delimiter between the cell and the environment, acting as one of the major constituients of the cellular 
plasma membrane~\cite{reece:2014:biobook}. The plasma membrane consists of a mixture of many lipid species, as
well as proteins and lipid-like molecules, and the mixture is tuned by the cell to adapt the 
structure and flexibility of the plasma membrane to different environments~\cite{pandit:2008:simulationtextbook,van:2008:lipidvariety,zhang:2008:memhomeo}. 
Furthermore, the cellular membrane is the interface for exchange
of nutrients with the environment, and also the interface for the transmission of signals to and from the outside of the cell. This
exchange is done through passive diffusion, proteins and other molecules embedded into the membrane, and through the formation
of vesicles and buds out of the lipid bilayer~\cite{reece:2014:biobook}. The behavior and function of the plasma membrane
is heavily dependent on the structure of the bilayer, which again can be influenced directly by the mixture of phospholipids constituting the
membrane~\cite{van:2008:lipidvariety,zhang:2008:memhomeo}.

@@

\begin{figure}[p]
\caption[Chemical structures of representative phospholipids highlighting the difference
between ether- and ester-links.]{ 
Chemical structures of representative phospholipids highlighting the difference 
between ether- and ester-links. POPC (1-palmitoyl-2-oleoyl-sn-glycero-3-phosphatidylcholine) is a 
diester lipid and HOPC (1-hexadecyl-2-(9-octadecenyl)-sn-glycero-3-phosphatidylcholine) is its diether analog that lacks fatty acid carbonyl groups.
}
\label{fig:struc}
\includegraphics[height=0.66\textheight]{images/Structure_annotated}
\end{figure}

@@

Computational methods like molecular often have to strike a balance between accuracy and computational feasibility --- approximations
to the interactions in a system can significantly reduce computational cost, and if carefully done can still result in
accurate reproduction of experimental results~\cite{pandit:2008:simulationtextbook}.

Molecular dynamics approximates systems by treating particles classically. Particles are expressed as points in space, 
with masses centered at the nucleus~\cite{pandit:2008:simulationtextbook}.
Functional forms and terms to calculate the potential energy of systems are defined in a force-field.
Bonds and bond angles in molecules are modeled as harmonic potentials, and torisional parameters within molecules are modeled
using periodic functions. Non-bonded interactions
are modeled using simple pairwise-additive potentials and in general do not treat many-body interactions~\cite{tieleman:1997:memsim,pandit:2008:simulationtextbook}. 
Van der Waals (VdW) dispersion and hard-shell repulsion are usually treated using a Lennard-Jones 6-12 potential,
and short-range electrostatics are represented by a coulomb potential~\cite{tieleman:1997:memsim,pandit:2008:simulationtextbook}.
The potential terms are added together over the whole system of particles
to get the overall potential function of the system, which is then used to evolve the system over time by integrating
Newton's laws of motion~\cite{frenkel:2001:molsimbook}. An example of the total potential can be seen in equation~\ref{eq:mdpot}~\cite{pandit:2008:simulationtextbook}.
\begin{equation}
    \label{eq:mdpot}
\begin{aligned}
    V_{tot}=&\sum_{\text{bonds}}K_b(r-r_0)^2 \\+& \sum_{\text{angles}}K_{\theta}(\theta - \theta_0)^2 \\+& \sum_{\text{improper}}K_\Phi(\Phi-\Phi_0)^2
    \\+& \sum_{\text{torision}}K_\phi[1-cos(n\phi-\phi_0)] \\+& \sum_{\text{Estatic}}\frac{q_iq_j}{r_{ij}} \\+& \sum_{VdW}\frac{A_{ij}}{r^{12}_{ij}}-\frac{B_{ij}}{r^6_{ij}}
\end{aligned}
\end{equation}

Most force-fields for molecular dynamics treat charges on particles in the system as an average picture of overall electronic behavior, as the
timescale of electronic fluctuations is much smaller than the timescale of MD simulations; this means bonds are permanent,
and average charge densities are fixed to particles~\cite{pandit:2008:simulationtextbook}.
Some force fields treat electronic polarizability as an explicit term in the potential function~\cite{li:2017:drude,ponder:2010:current}; however in general
MD force-fields do not include this in order to improve computation speed, and it has been found that
~\cite{pandit:2008:simulationtextbook}.

To ensure accurate reproduction of experimental results from complex systems, 
force-fields are developed and optimized to directly reproduce experimental data
in simple model systems. To develop force-fields, systems of small molecules can be 
optimized to reproduce experimental heats and enthalpies of 
vaporization, molecular volumes, 
and densities of condensed phases~\cite{berger:1997,chiu:1999:optimization,chiu:2003:structure,chiu:2009}.
For systems of whole lipid bilayers, experimental methods such as deuterium NMR, small angle x-ray scattering, and small angle neutron scattering 
can be used to get ensemble average values for bilayer ordering and structure and are often used to 
validate lipid simulations~\cite{pandit:2008:simulationtextbook,fogarty:2015,chiu:2009,kruczek:2017:ether,kruczek:2017,leonard:2018,li:2017:drude,nagle:2000}.
We can also look at electrostatic properties such as the bilayer electrostatic dipole potentials~\cite{gawrisch:1992,berkowitz:2006:aqueous}, or mechanical
properties like bilayer compressibility or surface tension~\cite{kruczek:2017:ether,kruczek:2017,jahnig:1996:surface}.
For optimization of force-fields using small molecules, experimental heats and enthalpies of vaporization, molecular volumes, 
and densities of condensed phases can be usedv~\cite{berger:1997,chiu:1999:optimization,chiu:2003:structure,chiu:2009}.

@@

Berger \etal sought to further improve the densities given by the GROMOS force-field in 1997 
by optimizing VdW parameters using molecular volumes and
heats of vaporization in small hydrocarbon molecules to improve the acyl chains of DPPC~\cite{berger:1997},
work that was continued by Chiu \etal~\cite{chiu:1999:optimization,chiu:2003:structure}, 
Later, further optimization was carried out by Chiu \etal 
in 2009 to improve torisional and VdW parameters using experimental 
heats of vaporization and densities, and validated
the overall result by predicting small-angle x-ray scattering 
results for model lipid bilayers to create the GROMOS 43-A1S3 lipid force field which gave excellent reproduction of SAXS form-factors for
different lipids~\cite{chiu:2009}.

@@

We also use the electron denisty distribution to calculate the peak-to-peak distance $D_{hh}$, 
which is used another measure of the bilayer thickness. This is roughly reflective of the distance between the 
electron-dense phosphate groups on either bilayer leaflet.

@@

of 3.3~\AA, based on the radial distrubution functions of \na with the

@@

charge densitities of ions contained behind the surface. We chose to do this because all other parts of 

@@

\begin{figure}[p]
    \caption[Comparison of Gouy-Chapman theory predictions and simulation results.]{ 
Comparison of Gouy-Chapman theory predictions and simulation results. Theoretical distributions are given by the 
solid lines, and data from our simulations are shown as points with error bars. (a) and (c) show the electrostatic
potentials of each system. For clairity, we show error-bars for the simulation
results for every 13th point. The Debye-Huckle 
potentials shown follow the form given in equation~\ref{eq:gcpot}. (b) and (d) show the number density distribution
of ions in each system. Error-bars for the 
simulation results are shown
for every 30th point. Note that both systems are
translated to center around the solvent-occupied region of the box, giving an interspace region of \about 13 nm in
each system. Parameters used in Gouy-Chapman theory are in table~\ref{tab:gctheory} }
\label{fig:gctheory}
\includegraphics[width=\textwidth]{gouy.eps}
\end{figure}
We note a very close match between the two. Additionally, we find that HOPC shows a slightly 
larger $K$ than POPC, indicating a \about10\% 
shorter screening length for the system. This means that a bilayer of HOPC is better shielded from environmental electric fields.
The shorter screening length in the HOPC is also reflective of the smaller 
number of ions that adsorb onto the surface of the bilayer, as this directly results in a larger number density in bulk solvent due to the fixed number of ions in our system.

@@

In our work, we have found that ether-linked lipid bilayers show a distinct peak in solvent density
that is not disrupted by the inclusion of a moderate concentration of salt. This region
shows siginificantly reduced lateral diffusion, and longer autocorrelation times than the same
region in an analgous ester-linked lipid bilayer. Furthermore, we find that
the characteristic lower dipole potential of an ether-linked bilayer reported in previous work~\cite{kruczek:2017:ether} is 
increased to match that of the ester-linked bilayer in the presence of salt. We also find that,
with our new protocol for determining the interface boundary of the lipid bilayer,
our simulations model ion distributions and electrostatic potentials from Gouy-Chapman theory well. 
The shorter screening length in the
ether-linked system suggests better shielding from electric fields far 
from the bilayer compared to the ester-linked system. This is a result
of the ether-linked lipid bilayer's lower affinity for ions than the ester-linked analog.

>>>>

\documentclass[12pt,openany,final]{book}
\usepackage[letterpaper,margin=1in,footskip=0.25in]{geometry}
\fontfamily{cmr}
\usepackage[final]{changes}
\usepackage{lipsum}
\usepackage[nottoc]{tocbibind}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{flafter}
\usepackage{floatrow}
%\usepackage{floatflt}
\usepackage{placeins}
\usepackage{siunitx}
\usepackage{graphicx}
\graphicspath{{figures/}}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{appendix}
\usepackage{amsmath}
\usepackage{cases}
\usepackage{calc}
\usepackage{amssymb}
\usepackage{color}
\usepackage{enumitem}
\usepackage{soul}
\usepackage{indentfirst}
\usepackage{hyphenat}
\usepackage{xspace}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{lineno}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[superscript]{cite}
\usepackage{lineno}
\titleformat
{\chapter} % command
[display] % shape
{\centering\sc\LARGE} % format
{\centering Chapter \thechapter} % label
{0.2ex} % sep
{
} % before-code
\titlespacing*{\chapter}{0pt}{1in}{0.25in}
\titlespacing*{\section}{0pt}{0pt}{0pt}
\hbadness=99999
%\epstopdfDeclareGraphicsRule{.tga}{png}{.png}{
%    convert #1 \OutputFile
%}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}
%\newcommand{\cmpersec}{$\frac{\text{cm}}{\text{s}}$~}
\newcommand{\cmpersec}{cm/s~}
\newcommand{\etal}{\textit{et al.}}
\newcommand{\na}{Na\textsuperscript{+}~}
\newcommand{\cl}{Cl\textsuperscript{-}~}
\newcommand{\PM}{$\pm$~}
\newcommand{\invnm}{$\text{\si{\nm}}^{-1}$~}
\newcommand{\nmeter}{\si{\nm}~}
\renewcommand{\arraystretch}{1.8}
%\newcommand{\hl}{\added}
%\newcommand{\sout}{\deleted}
\newcommand{\TODO}{\hl{TODO}~}
\newcommand{\about}{$\sim$}
\newcommand{\aangstroms}{{\aa}ngstr{\"o}ms}
\newcommand{\aangstrom}{{\aa}ngstr{\"o}m}
\newenvironment{hle}{\color{red}}

@@

Polar lipids, or phospholipids, are present in all parts of cells
and are used in many signalling and structural roles.
As structural molecules they act as the main component of cellular plasma membranes --- bilayers
of polar lipids that separate cells from their environments. Bilayer properties are heavily
influenced by the structure of their component polar lipids, and different lipids
are found in different organisms. 
A distinguishing feature of Archaeal plasma membranes is that their phospholipids contain ether-links, as opposed to bacterial and eukaryotic plasma
membranes where phospholipids primarily contain ester-links. In our work we examine the effects of
salt on bilayer structure in the case of an ether-linked lipid bilayer. We use molecular dynamics simulations and compare equilibrium properties of two model lipid
bilayers in NaCl salt solution --- POPC and its ether-linked analog that we refer to as HOPC. We make the following key observations.
The headgroup region of HOPC~``adsorbs'' fewer ions compared to the headgroup region of POPC. Consistent with this,
we note that the Debye screening length in the HOPC system is \about 10\% shorter than that
in the POPC system. Herein, we introduce a protocol to identify the lipid-water interfacial boundary that
reproduces the bulk salt distribution consistent with
Gouy-Chapman theory. We also note that the HOPC bilayer has excess solvent
in the headgroup region when compared to POPC,
coinciding with a trough in the electrostatic potential. Waters in
this region have longer autocorrelation times and smaller lateral diffusion rates compared to the corresponding region
in the POPC bilayer, suggesting that the waters in HOPC are more strongly
coordinated to the lipid headgroups. Furthermore, we note that it is this
region of tightly coordinated waters in the HOPC system that has a lower density of Na$^+$ ions.
Based on these observations we conclude that an ether-linked lipid bilayer has a lower binding
affinity for Na$^+$ compared to an ester-linked lipid bilayer.

@@

\section{Ether- and Ester-linked Phospholipids}
Phospholipids are a diverse species of biological molecules used in many roles in life~\cite{van:2008:lipidvariety}. These molecules
are amphipathic, with a headgroup that is hydrophillic attached to hydrophobic acyl chains by a
glycerol backbone~\cite{pandit:2008:simulationtextbook,israelachvili:2011:intermol}. 
These molecules, when above a critical concentration in aqueous solution, self assemble into
various aggregate structures in order 
to reduce the exposure of the hydrophobic chains
to polar solvent --- these structures include
micelles, vesicles, and bilayers along with others~\cite{israelachvili:2011:intermol}. 
Phospholipids tend to form bilayers, 
where the hydrophillic headgroups face the solvent and the 
hydrophobic acyl chains face into the center 
of the structure~\cite{israelachvili:2011:intermol,ashrafuzzaman:2012:membrane}. 
An image of a bilayer of a commonly studied
model lipid can be seen
in figure~\ref{fig:boximage}.
\begin{figure}[htp]
    \caption[Image of a model bilayer of phospholipids from a simulation.]{ Image of a model bilayer of phospholipids from a simulation. The lipids can be seen
in the center of the image, with the hydrophobic chains colored in
light purple. The polar headgroup can be seen highlighted by the phosphate group in orange and the choline nitrogen in blue
facing the solvent. Solvent molecules have been removed for clarity. Figure generated
using VMD~\cite{vmd}}
\label{fig:boximage}
\includegraphics[height=0.25\textheight]{images/popc_image}
\end{figure}
In living cells, lipid bilayers act as the delimiter between the cell and the environment, acting as one of the major constituents of the cellular 
plasma membrane~\cite{reece:2014:biobook}. The plasma membrane consists of a mixture of many lipid species, as
well as proteins and lipid-like molecules, and the mixture is tuned by the cell to adapt the 
structure and flexibility of the plasma membrane to different environments~\cite{pandit:2008:simulationtextbook,van:2008:lipidvariety,zhang:2008:memhomeo}. 
Furthermore, the cellular membrane is the interface for exchange
of nutrients with the environment, and also the interface for the transmission of signals to and from the outside of the cell. This
exchange is done through passive diffusion, proteins and other molecules embedded into the membrane, and through the formation
of vesicles and buds out of the lipid bilayer~\cite{reece:2014:biobook}. The behavior and function of the plasma membrane
is heavily dependent on the structure of the bilayer, which again can be influenced directly by the mixture of phospholipids constituting the
membrane~\cite{van:2008:lipidvariety,zhang:2008:memhomeo}.

@@

\begin{figure}[htp]
\caption[Chemical structures of representative phospholipids highlighting the difference
between ether- and ester-links.]{ 
Chemical structures of representative phospholipids highlighting the difference 
between ether- and ester-links. POPC (1-palmitoyl-2-oleoyl-sn-glycero-3-phosphatidylcholine) is a 
diester lipid and HOPC (1-hexadecyl-2-(9-octadecenyl)-sn-glycero-3-phosphatidylcholine) is its diether analog that lacks fatty acid carbonyl groups.
}
\label{fig:struc}
\includegraphics[height=0.5\textheight]{images/Structure_annotated}
\end{figure}

@@

%Computational methods like molecular dynamics often have to strike a balance between accuracy and computational feasibility.--- approximations
%to the interactions in a system can significantly reduce computational cost, and if carefully done can still result in
%accurate reproduction of experimental results~\cite{pandit:2008:simulationtextbook}.
Computational methods like molecular dynamics must strike a balance between computational cost and accuracy. The most expensive
computations using \emph{ab initio} methods with minimal approximations are the most accurate, but are only feasible for very small systems~\cite{dror:2012:biomicroscope}.
For biologically relevant systems, a classical approximation is able to reproduce most important phenomena~\cite{pandit:2008:simulationtextbook,dror:2012:biomicroscope}..
MD makes this classical approximation, expressing particles as points in space, 
with masses centered at the nucleus~\cite{pandit:2008:simulationtextbook}.
Functional forms and functional parameters needed to calculate the hamiltonian of systems are defined in a force-field.
Bonds and bond angles are modeled as harmonic potentials, and torsional parameters within molecules are modeled
using periodic functions. Non-bonded interactions
are modeled using simple pairwise-additive potentials and generally do not treat many-body interactions~\cite{tieleman:1997:memsim,pandit:2008:simulationtextbook}. 
Van der Waals (VdW) dispersion and hard-shell repulsion are usually treated using a Lennard-Jones 6-12 potential,
and short-range electrostatics are represented by a coulomb potential~\cite{tieleman:1997:memsim,pandit:2008:simulationtextbook}.
The potential terms are added together over the whole system of particles
to get the overall potential function of the system, which is then used to evolve the system over time by integrating
Newton's laws of motion~\cite{frenkel:2001:molsimbook}. An example of the total potential can be seen in equation~\ref{eq:mdpot}~\cite{pandit:2008:simulationtextbook}.
\begin{equation}
    \label{eq:mdpot}
\begin{aligned}
    V_{tot}=&\sum_{\text{bonds}}K_b(r-r_0)^2 \\+& \sum_{\text{angles}}K_{\theta}(\theta - \theta_0)^2 \\+& \sum_{\text{improper}}K_\Phi(\Phi-\Phi_0)^2
    \\+& \sum_{\text{torision}}K_\phi[1-cos(n\phi-\phi_0)] \\+& \sum_{\text{Estatic}}\frac{q_iq_j}{r_{ij}} \\+& \sum_{VdW}\frac{A_{ij}}{r^{12}_{ij}}-\frac{B_{ij}}{r^6_{ij}}
\end{aligned}
\end{equation}

Most force-fields for molecular dynamics treat charges on particles in the system as an average picture of overall electronic behavior, as the
timescale of electronic fluctuations is much smaller than the timescale of MD simulations; this means bonds are permanent,
and average charge densities are fixed to particles~\cite{pandit:2008:simulationtextbook}.
Some force fields treat electronic polarizability as an explicit term in the potential function~\cite{li:2017:drude,ponder:2010:current}; however
most MD force-fields do not include this while still giving a good reproduction of experimental results~\cite{pandit:2008:simulationtextbook,chiu:2009,leonard:2018}.

To ensure accurate reproduction of experimental results from complex systems, 
force-fields are developed and optimized to directly reproduce experimental data
in simple model systems. To develop force-fields, systems of small molecules can be 
optimized to reproduce experimental heats and enthalpies of 
vaporization, molecular volumes, 
and densities of condensed phases~\cite{berger:1997,chiu:1999:optimization,chiu:2003:structure,chiu:2009}.
For systems of whole lipid bilayers, experimental methods such as deuterium NMR, small angle x-ray scattering, and small angle neutron scattering 
can be used to get ensemble average values for bilayer ordering and structure and are often used to 
validate lipid simulations~\cite{pandit:2008:simulationtextbook,fogarty:2015,chiu:2009,kruczek:2017:ether,kruczek:2017,leonard:2018,li:2017:drude,nagle:2000}.
We can also look at electrostatic properties such as the bilayer electrostatic dipole potentials~\cite{gawrisch:1992,berkowitz:2006:aqueous}, or mechanical
properties like bilayer compressibility or surface tension~\cite{kruczek:2017:ether,kruczek:2017,jahnig:1996:surface}.
For optimization of force-fields using small molecules, experimental heats and enthalpies of vaporization, molecular volumes, 
and densities of condensed phases can be used~\cite{berger:1997,chiu:1999:optimization,chiu:2003:structure,chiu:2009}.

@@

Berger \etal sought to further improve the densities given by the GROMOS force-field in 1997 
by optimizing VdW parameters using molecular volumes and
heats of vaporization in small hydrocarbon molecules to improve the acyl chains of DPPC~\cite{berger:1997},
work that was continued by Chiu \etal~\cite{chiu:1999:optimization,chiu:2003:structure}, 
Later, further optimization was carried out by Chiu \etal 
in 2009 to improve torsional and VdW parameters using experimental 
heats of vaporization and densities, and validated
the overall result by predicting small-angle x-ray scattering 
results for model lipid bilayers to create the GROMOS 43-A1S3 lipid force field which gave excellent reproduction of SAXS form-factors for
different lipids~\cite{chiu:2009}.

@@

We also use the electron density distribution to calculate the peak-to-peak distance $D_{hh}$, 
which is used another measure of the bilayer thickness. This is roughly reflective of the distance between the 
electron-dense phosphate groups on either bilayer leaflet.

@@

of 3.3~\AA, based on the radial distribution functions of \na with the

@@

charge densities of ions contained behind the surface. We chose to do this because all other parts of 

@@

\begin{figure}[p]
    \caption[Comparison of Gouy-Chapman theory predictions and simulation results.]{ 
Comparison of Gouy-Chapman theory predictions and simulation results. Theoretical distributions are given by the 
solid lines, and data from our simulations are shown as points with error bars. (a) and (c) show the electrostatic
potentials of each system. For clarity, we show error-bars for the simulation
results for every 13th point. The Debye-Huckle 
potentials shown follow the form given in equation~\ref{eq:gcpot}. (b) and (d) show the number density distribution
of ions in each system. Error-bars for the 
simulation results are shown
for every 30th point. Note that both systems are
translated to center around the solvent-occupied region of the box, giving an interspace region of \about 13 nm in
each system. Parameters used in Gouy-Chapman theory are in table~\ref{tab:gctheory} }
\label{fig:gctheory}
\includegraphics[width=\textwidth]{gouy.eps}
\end{figure}
We note a very close match between the two. Additionally, we find that HOPC shows a slightly 
larger $K$ than POPC, indicating a \about10\% 
shorter screening length for the system. This means that a bilayer of HOPC is better shielded from environmental electric fields.
The shorter screening length in the HOPC is also reflective of the smaller 
number of ions that adsorb onto the surface of the bilayer, as this directly results in a larger number density in bulk solvent due to the fixed number of ions in our system.

@@

In our work, we have found that ether-linked lipid bilayers show a distinct peak in solvent density
that is not disrupted by the inclusion of a moderate concentration of salt. This region
shows significantly reduced lateral diffusion, and longer autocorrelation times than the same
region in an analogous ester-linked lipid bilayer. Furthermore, we find that
the characteristic lower dipole potential of an ether-linked bilayer reported in previous work~\cite{kruczek:2017:ether} is 
increased to match that of the ester-linked bilayer in the presence of salt. We also find that,
with our new protocol for determining the interface boundary of the lipid bilayer,
our simulations model ion distributions and electrostatic potentials from Gouy-Chapman theory well. 
The shorter screening length in the
ether-linked system suggests better shielding from electric fields far 
from the bilayer compared to the ester-linked system. This is a result
of the ether-linked lipid bilayer's lower affinity for ions than the ester-linked analog.
